### 2014-03-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update report and images, add run all script
Chicago Fire: add 2 figures, update report

In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions). The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur. The dash-dotted line is the prescribed FDS input HRR. We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR. The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited. The HRR drops to 5 MW as the available oxygen inside the structure gets consumed. There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents. Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s. After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW. The HRR then begins to increase towarda a sustainable steady state value.

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door.

\begin{figure}[h!]
\centering
\includegraphics[width=.80\textwidth]{../Figures/smv_exterior_fire}
\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
\label{fig:smv_ext_fire}
\end{figure}

\section{Temperature}

\begin{figure}[h!]
\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_129}
\input{../Scripts/colorbar_metric} 
\caption{Temperature 1 second prior to rear door opening.}
\label{fig:temp_129s}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_159}
\input{../Scripts/colorbar_metric} 
\caption{Temperature 1 second prior to interior door failing.}
\label{fig:temp_159s}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_metric} 
\caption{Temperature 1 second after interior door fails.}
\label{fig:temp_161s}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature 15 seconds after interior door fails.}
\label{fig:temp_175s}
\end{figure}

>>>>

In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions). The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur. The dash-dotted line is the prescribed FDS input HRR. We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR. The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited. The HRR drops to 5 MW as the available oxygen inside the structure gets consumed. There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents. Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s. After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW. The HRR then begins to increase towards a sustainable steady state value.

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door. Therefore, further more detailed analysis will focus on the results of the baseline simulation results.

\begin{figure}[h!]
\centering
\includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
\label{fig:smv_ext_fire}
\end{figure}

\section{Temperature}
The focus area for analysis of the temperature simulation results are the attic, the rear porch and connecting stairwell, and the interior hallways which connects the rear porch to the front stairwell.

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature from baseline simulation, 1 second prior to rear door opening.}
\label{fig:temp_129s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature from baseline simulation, 1 second prior to interior door failing.}
\label{fig:temp_159s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature from baseline simulation, 1 second after interior door fails.}
\label{fig:temp_161s}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
\input{../Scripts/colorbar_std} 
\input{../Scripts/colorbar_metric}
\caption{Temperature from baseline simulation, 15 seconds after interior door fails.}
\label{fig:temp_175s}
\end{figure}
